Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging

### 2020-06-19 article.tex
More revisions

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology. In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI). We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions. Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchymal perfusion. These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
\end{abstract}

@@

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. However, to date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to anesthetized state. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2x magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b. The width of the two vessels remained steady throughout the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd). Calculated using 50 MESI frames acquired immediately before and after the continuous imaging session.
    }
\end{figure}

The repeatability of these measurements were further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}. Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states over three separate imaging sessions lasting 30 minutes each. Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics. On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%). The perfusion of parenchymal regions increased on average by 80\% across all three subjects.

% Figure 3 - Awake to Anesthetized Results Summary
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure3.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:summary}
        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Each row of charts depicts vessel diameter, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states averaged across three different imaging sessions for each animal (mean $\pm$ sd).
    }
\end{figure}

>>>>

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology. In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI). We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions. Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchyma perfusion. These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
\end{abstract}

@@

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) of photothrombotic stroke observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. However, to date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to the anesthetized state. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2$\times$ magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure LSCI (5 ms) and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b. The width of the two vessels remained steady throughout the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Figs.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to the isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 1 mm). Dashed lines indicate the cross-sectional profiles used to calculate vessel width. Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal across four imaging sessions (mean $\pm$ sd).
    }
\end{figure}

The repeatability of these measurements were further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}. Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states across three separate imaging sessions lasting 30 minutes each. Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics. On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%). The perfusion of parenchymal regions increased on average by 80\% across all three subjects.

% Figure 3 - Awake to Anesthetized Results Summary
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure3.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:summary}
        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis (Scale bar = 1 mm). Dashed lines indicate the cross-sectional profiles used to calculate vessel width. Each row of charts depicts vessel diameter, vascular flux, and parenchyma tissue perfusion during awake and anesthetized states averaged across three separate imaging sessions for each animal (mean $\pm$ sd).
    }
\end{figure}
